% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{hyperref}
\usepackage{array}


%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{-7pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}}
%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Itamar Amith} & \textbf{Mobile: \texttt{+}61 402 610 969} \\
Solutions Architect & itamaram@gmail.com \\
Melbourne, VIC & \href{http://www.linkedin.com/in/itamaramith}{http://www.linkedin.com/in/itamaramith}\\
 & \href{https://github.com/itamaram/}{https://github.com/itamaram/}
\end{tabular*}
\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Personal Statement}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{center}
  \parbox{6.762in}{ I am a hands-on problem solver with 10 years of industry experience as well as a strong academic background. I'm particularly adept in translating requirements to high level technical designs, while addressing business concerns such as scalability, availability, tech debt and potential blockers. \linebreak
  In my spare time I enjoy developing intelligent autonomous agents for online games, attending live music shows, and trying to explain to my mom what it is I do for a living.}
  \end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Employment History}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item[]
    \ressubheading{Contract Work}{Melbourne, AU}{Freelance Consultant}{March 2020 - Current}
    
    While attempting to create the next big thing in my garage, I also work as a freelancer. I specialising in consulting for startups lacking strong internal tech leadership, and creating bespoke solutions for small businesses.
    A few notable projects are:
    
    \begin{itemize}
        \resitem{\textbf{Bakery For Sophia} - Converted the entire operations aspect of the business from a collection of unwieldy Excel spreadsheets to a custom tailored platform built from the grounds up, working closely with the owners to keep what was working and improve on what was not. The new system saves over 300 hours of labour a month for the business. The solution was implemented in dotnet running on a serverless Azure stack.}
        \resitem{\textbf{PointsBet} - Due to the team responsible for the statistical modeling working exclusively in Python, and the dev team working only in dotnet, invoking statistical computations from within code flows was cumbersome and was generally avoided. I designed and implemented a generic solution which streamlined the work flow of the stats team, and resulted in their models being deployed as containerised micro-services allowing for seamless interoperability with any other service.}
        \resitem{\textbf{CultureAmp} - A Microsoft Outlook plugin needed immediate attention as system updates destabilised it on some environment. The plugin is written in dotnet and WPF using the Add-in Express framework. The solution involved creative conditional embedding of components based on the user OS.}
    \end{itemize}
    
\item[]
    \ressubheading{Restoke.ai}{Melbourne, AU}{Co-Founder, Head of Development}{June 2019 - June 2020}
    Restoke.ai is a back-of-the-house management platform for hospitality businesses which assists in streamlining the capturing of operational data. Restoke then provides AI driven insights to optimise the business performance.
    
    \begin{itemize}
        \resitem{Bootstrapped the entire platform in-house with one other developer, using Python and Django deployed on AWS EC2 instances.}
        \resitem{Gather requirements for MVP as well as future development road map by liasing with prospective (and later current) customers.}
        \resitem{Communicate with investors and accelerators in order to secure funding.}
    \end{itemize}
    
\item[]
    \ressubheading{PointsBet Australia}{Melbourne, AU}{Solutions Architect}{April 2019 - October 2019}
    
    In recognition of my achievements in the architecture space, I've been promoted and was given a more hands off role, allowing me to focus my full attention on delivering design artefacts, as well as evaluating new technologies for future and current initiatives, and generating proof of concept projects to allow both for assessing viability, and providing boilerplate code for the engineers.
    My most impactful projects were:
    
    \begin{itemize}
        \resitem{Compare and contrast options for a unified single sign on solution across physical regions, including a hand rolled bespoke solution and third party providers. Engaging both business stakeholders and engineers, I've provided sample implementation for each candidate, as well as a cost and capabilities analysis.}
        \resitem{Introduce a multi-cloud strategy, allowing the dev team to leverage the unique offering of different providers, cutting down development time. The first project to use this strategy used Google Firebase storage in in conjuction with an Azure dotnet backend, which saved weeks in implementation of front end synchronisation.}
    \end{itemize}
    
\item[]
	\ressubheading{PointsBet Australia}{Melbourne, AU}{Solutions Lead}{July 2018 - April 2019}
	
	As PointsBet grew, so did my responsiblities, as did the team I was leading. The business problems I needed to implement solutions for became increasingly vague, and my role now included working out requirements as well as coming up with satisfactory business solutions and seeing them through technical implementation.
	
    \begin{itemize}
    	\resitem{Communicate regularly with product management as well as stakeholders to transition visions into results, while constantly negotiating over changing scopes, and contested development resources.}
    	\resitem{Use online task management tools to better track and consequently utilise developer's time across teams and projects, this allowed for justifying the hiring of additional heads.}
    	\resitem{Champion the development of a component responsible for the ingestion of an external odds feed into our bet management system. The deployed result was durable, reliable, performant and self-error-correcting.}
    	\resitem{Use a mixed team of contractors and full-time devs to deliver a bespoke data processing pipeline responsible for the generation of all spread markets on the site by deriving existing markets using statistical modeling.}
    \end{itemize}
	
\item[]
	\ressubheading{PointsBet Australia}{Melbourne, AU}{Technical Lead}{July 2017 - July 2018}
	
	PointsBet is an ambitious sports gaming scale up, with an aggressive international growth strategy. I've joined the company when it had just a handful of engineers, and an off the shelf code base. It is a Microsoft shop through and through and is heavily reliant on Azure's cloud offering. Since I've joined the team, I've was able to accomplish the following:
	
	\begin{itemize}
		\resitem{Experience a wide range of Azure products, both for SaaS, and IaaS (focusing mainly on CosmosDB, ServiceBus, and Function Apps)}
		\resitem{Planned and executed a piecewise migration from a stored proc reliant T-SQL database to managed code, while ensuring the system usability and stability at every step was not impacted.}
		\resitem{Positively influenced the technical direction of the company through design discussions, and negotiating compromises acceptable to both the business and the dev team in the face of looming deadlines.}
		\resitem{Adapted quickly to rapidly changing requirements by designing solutions composed of small generic deliverables, ensuring minimal amount of work was lost when projects were modified or rescheduled.}
	\end{itemize}
	
\item[]
	\ressubheading{Carsales.com}{Melbourne, AU}{Solutions Architect}{September 2015 - May 2017}

	While still actively developing Ryvuss, my expertise is further leveraged to assist other teams in designing and implementing software solutions as well as help improve existing ones. My major achievments while on in thie role are:
	\begin{itemize}
		\resitem{Worked closely with the membership team to teach best practices, implement a CD system, and pave the path towards true microservices architecture in the cloud}
		\resitem{Provided guidance to the retail team in their development of their new global platform, allowing Carsales to scale horizontally into international markets}
		\resitem{Oversaw the integration project with SoloAutos.mx, Carsales' first international acquisition}
	\end{itemize}
	
\item[]
	\ressubheading{Carsales.com (Ryvuss Search)}{Melbourne, AU}{Senior Software Engineer}{August 2013 - May 2017}
	
	Ryvuss is a bespoke faceted search engine, written in house in order to meet Carsales' exact needs. All code contribution to this project must be extremely performant in terms of both resource consumption as well as execution speed, in a highly concurrent environment. Some of my key achievements in this role are:

	\begin{itemize}
		\resitem{Designed and implemented a geospatial index, allowing querying for items based on polygon-shaped area constraints, as well as sort by distance from a given point.}
		\resitem{Completely rewrote the existing solution for range indexes, allowing for better performance when filtering search based on a numerical range.}
		\resitem{Co-authored an improved query language to be used by the engine.}
		\resitem{Built a new version of the navigation component from the ground up, which allows constructing complex hierarchical queries in a fully data driven manner.}
		\resitem{Created a generic extensible module, allowing complex searches to be efficiently mapped to SEO urls}
		\resitem{Spent two weeks on site at Encar SK(South Korea) setting up an instance of Ryvuss running completely in AWS}
		\resitem{Worked with engineers from other teams to assist with consumption of Ryvuss as well as assistance with general application architecture and design.}
		\resitem{Participated in strict code reviews, as both reviewer and reviewee, at all stages of the software life cycle to ensure optimal outcome.}
	\end{itemize}

\item[]
	\ressubheading{POLi Payments}{Melbourne, AU}{Software Developer}{July 2012 - July 2013}
	
	POLi Payments is a online payment gateway which facilitates transactions by automating a transfer through the user's online banking platform. 
	\begin{itemize}
		\resitem{Contributed to a sophisticated inhouse JS library used for imitating client actions used on live sites which were rapidly, and constantly changing.}
		\resitem{Extended an existing framework for compiling XML documents into JavaScript code and equivalent C\# code.}
		\resitem{Upgraded several highly functional websites from asp.net to MVC3, while maintaining full backwards compatibility with existing APIs, as well as adding new features.} 
		\resitem{Maintained, patched and upgraded a the DB layer of the application, composed of an extensive collection of T-SQL stored procedures.}
	\end{itemize}
	
\item[]
	\ressubheading{Investit Ltd}{Auckland, NZ}{Full Stack .NET Developer}{Oct. 2010 - June 2012}

	Investit (NZ) is a highly functional, high volume, transaction finance website, which allowed users to start an auction for their investment capital, and get bids from financial institutions for different terms.
	\begin{itemize}
		\resitem{Build the user registration system from specification, allowing for different type of entities (Personal, joint, trusts etc), each requiring its own complex validation rules}
		\resitem{Write a configurable module which automatically fills in pdf forms for the users based on their details.}
		\resitem{Code all the front end Javascript, including the auction page to efficiently poll for new bids as well as auction status and update page accordingly}
		\resitem{Developed internal analytics tools drawing from optimized HQL queries and displaying using Google's Chart Tool's web API.}
	\end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item[]
	\ressubheading{University of Auckland}{Auckland, NZ}{MSc in Computer Science}{2009 - 2010}
	\begin{itemize}
		\resitem[]{Advisor: Dr. Michael J. Dinneen}
		\resitem[]{Thesis: Minimal membership automata for families of bounded treewidth}
		\resitem[]{Graduated with Second Class Honours, Second Division}
	\end{itemize}

\item[]
	\ressubheading{University of Auckland}{Auckland, NZ}{BSc (Hons) in Mathematics}{2008 - 2009}
	\begin{itemize}
		\resitem[]{Advisor: Dr. Jamie Sneddon}
		\resitem[]{Dissertation: Scoring incomplete tournaments}
		\resitem[]{Graduated with Second Class Honours, Second Division}
	\end{itemize}

\item[]
	\ressubheading{University of Auckland}{Auckland, NZ}{BSc in Applied Mathematics, Computer Science, and Mathematics}{2005 - 2008}

\end{itemize}

\end{document}
